\documentclass{book}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{ulem}
\usepackage{ntilatexmacros}
\usepackage{ntiassessment}
\usepackage{amsmath}
\usepackage{stmaryrd}
\begin{document}
\textbf{New References }

[1]P. Yang and Q. Zhu, "Finding key attribute subset in data set for outlier detection," \textit{Knowledge Base Systems, }vol. 24, pp. $269 - 274$, 2011.

[2]T. E. Senator, H. G. Goldberg, and A. Memory, "Disthingushing the Unexplainable from the Merely Unusual: Adding Explanations to Outliers to Discover and Detect Significant Complex Rare Events," in \textit{ODD }Chicago, IL USA, 2013, pp. 40-45.

[3]F. Rasheed and R. Alhajj, "A Framework for Periodic Outlier Detection in Time Series Sequences," \textit{IEEE Transactions on Cybernetics, }pp. 1-14, 2013.

[4]W. Liu, Y. Zheng, S. Chawla, J. Yuan, and X. Xing, "Discovering spatio-temporal causal interactions in traffic data streams," in \textit{Proceedings of the 17th ACM SIGKDD international conference on Knowledge discovery and data mining}, San Diego, California, USA, 2011, pp. 1010-1018.

[5]H. Lin and Q. Zhu, "Detecting Outlying Subspaces of Exceptional Objects in Nominal Data Sets," \textit{Journal of Computational Information System, }vol. 7, pp. 3071-3079, 2012.

[6]A. B. Koehler, R. D. Snyder, J. K. Ord, and A. Beaumont, "A study of outliers in the exponential smoothing approach to forecasting," \textit{International Journal of Forecasting, }vol. 28, pp. 477-484, 2012.

[7]B. Huang and P. Yang, "Finding key knowledge attribute subspace of outliers in high-dimensional dataset," \textit{Expert System with Application, }vol. 38, pp. $10147 - 10152$, 2011.

[8]M. Gebski, A. Penev, and R. K. Wong, "Grouping Categorial Anomalies," in \textit{International Conference on Web Intelligence and Intelligent Agent Technology}, 2008, pp. 411-414.

[9]S. Chen, W. Wang, and H. v. Zuylen, "A comparison of outlier detection algorithms for ITS data," \textit{Expert System with Application, }vol. 37, pp. 1169-1178, 2010.

[10]V. Chandola, A. Banerjee, and V. Kumar, "Anomaly Detection: A Survey," \textit{ACM Computing Surveys }vol. 41, pp. 1-58, 2009.

[11]S. Babbar and S. Chawla, "Mining Casual Outliers using Gausian Bayesian Networks," in \textit{International Confrence on Tools with Artificial Intelligence}, 2012, pp. 97-104.

[12]F. Angiulli, F. Fassetti, and L. Palopoli, "Detecting outlying properties of exceptional objects," \textit{ACM Trans. Database Syst., }vol. 34, pp. 1-62, 2009

\end{document}
